The Globular Cluster System of the Auriga Simulations

### 2019-03-24 AurigaGCS.tex
Wrote paragraph0 of the introduction

\section{Introduction}
\todo[inline]{Paragraph: General introduction of GCs}
\begin{itemize}
    \item GCs are old, ubiquitous, bright, `simple' single-age stellar populations
    \item GC properties (particularly metallicity) set by birth gas properties, 
        GC properties correlate with their host galaxy properties.
    \item The above makes GCs excellent proxies to study galform
    \item But first GCform should be understood
\end{itemize}
% Globular clusters (GCs) are old, ubiquitous, and bright. 
% GC ages range from $6-14$~Gyr, although observational age-estimates can be 
% uncertain and a definitive age threshold to classify star clusters as `globular' 
% remains topic of debate.
% GCs are observed at scales ranging from clusters of galaxies down to 
% dwarf galaxies 
% \todo[inline]{
%     \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
% }
% 
% The properties of the GCs themselves are correlated with those of their host
% galaxies, in particular their metallicities. 
% \todo[inline]{
%     `The mean metallicities of GC systems have long been 
%     known to scale with the metallicity of their host (van den Bergh
%     1975; Brodie \& Huchra 1991)' \citep[from][]{2008ApJ...681..197P}
% }

\todo[inline]{Paragraph: Theories of GC formation}
\begin{itemize}
    \item Special conditions in early Universe?
    \item Formation in collapsing proto-galaxies (in-situ-ish?)
    \item Formation as a result of (wet) mergers?
    \item Formation in satellites that are later accreted?
    \item No special conditions at high z, but connection between low-z YMC-
        and high-z GC-formation where differences could result from Hubble time
        of evolution?
    \item This means that in order to test formation models against observations,
        one not only needs needs to model GC formation, but also include the full 
        evolution over their lifetime in a cosmological tidal field.
\end{itemize}

>>>>

\section{Introduction}
Globular clusters (GCs) are old, ubiquitous, bright, and amongst the simplest
stellar configurations in the Universe. They inherit properties from their natal
gas, and the properties of globular cluster systems correlate with those of
(the field stars in) their host galaxies. In theory, this means that GC systems 
are excellent tracers of the formation and evolution of their host galaxies, if 
the formation of the GCs themselves is well-understood.

\todo[inline]{Paragraph: Theories of GC formation}

\begin{itemize}
    \item Special conditions in early Universe?
    \item Formation in collapsing proto-galaxies (in-situ-ish?)
    \item Formation as a result of (wet) mergers?
    \item Formation in satellites that are later accreted?
    \item No special conditions at high z, but connection between low-z YMC-
        and high-z GC-formation where differences could result from Hubble time
        of evolution?
    \item This means that in order to test formation models against observations,
        one not only needs needs to model GC formation, but also include the full 
        evolution over their lifetime in a cosmological tidal field.
\end{itemize}
